\documentclass{ExpressiveResume}
\usepackage{bookmark} % For handling bookmarks efficiently

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Zeyuan,
    lastname=Ding,
    email=zd2466@nyu.edu,
    phone=551-362-7194,
    linkedin=zeyuan0123,
    github=dingfengkun,
    city=Jersey City,
    state=NJ
]

\intro{
    Intellectually curious Master's student with 3+ years of academic experience in Algorithms and machine learning. Passionate about pursuing roles in Data Science or Machine Learning Engineering, with a focus on leveraging machine learning and causal inference to solve complex business challenges. In my free time, I enjoy playing table tennis.
}
% ----- Education -----
\section{Education}

\experience{Master of Science}{Data Science}{Sep 2024}{May 2026}{
    \noindent New York University, Center for Data Science \newline
    \begin{tabular}{l l l}
        Big Data & Mathematical Statistics & Data Programming \\
        Causal Inference & Linear Algebra and Optimization & Probability and Statistics for Data Science \\
    \end{tabular}
}

\experience{Bachelor of Advanced Computing (Honours)}{Computer Science}{July 2020}{June 2024}{
    \noindent University of Sydney, Faculty of Engineering \hfill GPA: 3.9/4.0 \newline
    \begin{tabular}{l l l}
        Artificial Intelligence (ML and DL) & Data Structures and Algorithms & Computational Geometry \\
        Software Engineering & Linear Algebra & Probability and Statistics \\
    \end{tabular}
}

% ----- Work Experience -----
\section{Work Experience}

\experience{Research Assistant}{Shanghai Qi Zhi Institute}{Aug 2021}{March 2022}{
    \achievement{
        Researched neural network (NN) compression and design space exploration for FPGA-based NN accelerators.
    }
    \achievement{
        Conducted simulation experiments, testing, and partial Chisel code implementation under Prof. Li Jiang at SJTU.
    }
}

\experience{Research Assistant}{Shanghai Jiao Tong University (Remote)}{Nov 2022}{Feb 2023}{
    \achievement{
        Assisted in improving the robustness and efficiency of Spiking Neural Networks (SNN) with attacking algorithms in ML and DL.
    }
    \achievement{
        Worked under the guidance of Profs. Fangxin Liu and Li Jiang in the Advanced Computer Architecture Lab.
    }
}

\experience{Honours Research Student}{University of Sydney}{July 2023}{June 2023}{
    \achievement{
        Developed a novel local routing algorithm for the $\theta_5$-graph with bounded path length under Prof. André Van Renssen.
    }
    \achievement{
        Designed and implemented a verification platform in JavaScript for algorithm accuracy; achieved distinction for the thesis.
    }
}

% ----- Technical Projects -----
\section{Technical Projects}

\experience{Bush Fire Risk Analysis}{Team Project}{Spring 2021}{Spring 2021}{
    \achievement{
        Built a bushfire risk analysis system using PostgreSQL, PostGIS, and Python with data from Australian government sources.
    }
    \achievement{
        Developed custom risk scoring algorithms considering population density, land use, and demographics.
    }
    \achievement{
        Visualized risk distribution with choropleth maps for New South Wales.
    }
}

\experience{3D File Conversion Engine}{Individual Project}{Fall 2022}{Fall 2022}{
    \achievement{
        Designed a high-performance 3D file conversion engine for the USYD TechLab, improving efficiency by 60\%.
    }
    \achievement{
        Built the AWS-based platform using Docker, ImageJ, and Python multiprocessing.
    }
}

% ----- Activities -----
\section{Activities}

\experience{Academic Paper Co-Author}{}{2023}{2023}{
    \achievement{
        Co-authored \textit{"Classroom AR Integration"}, published in \textit{Advances in Social Science and Culture}, Volume 5, No. 4.
    }
}

\end{document}
